### 2024-06-26 manuscript.Rmd
added Artner

Computational results, including those from statistical data analyses, are considered _reproducible_ if the same computation on the same data yields the same results if performed on a different computer or on the same computer later in time. Reproducibility is a prerequisite for replicable, robust and credible research in digital environments [@epskamp2019reproducibility; @hardwicke2018data].
 Various approaches have been suggested to increase chances of reproducibility of statistical data analyses in the R language [@peikert2021reproducible; @renv2022; @chan2023rang; @nagraj2023pracpac].
 Many approaches rely on R Markdown [@rmarkdown2023].
R Markdown is a simple language, which allows mixing natural language, simple formatting instructions (e.g., what is a headline, what should appear in bold face, what are list elements) and computer code (R, python or others) in a single document [@xie2018r].
When ever the document is reproduced, all of its computer code chunks are executed and thus generate dynamic content in the document.
This is particularly interesting for quantitative research reports, as  statistical results and contents of tables and figures can be dynamically generated. 
Packages like `papaja` [@R-papaja] or `stargazer` [@R-stargazer] further extend R Markdown's capabilities to format documents (including tables and figures) in a specific journal style, such as APA style.
Also, (R) Markdown forms the basis of _executable research articles_ [@tsang2020welcome], a browser-based form of research articles that allows authors to enrich their publications with interactive elements, such as figures or results that dynamically change based on readers' input.
A particular advantage of using R Markdown for creating research reports is that it helps avoiding common threats to reproducibility of statistical results, first and foremost, copy&paste errors between results of a regular R script and a scientific report (e.g., a reported statistic or table in a Word document) [@peikert2021reproducible];
further, it is suitable to generate a variety of scientific assets other than manuscripts such as posters [@posterdown2019], presentations [@xaringan2022], resumés [@vitae2023] or preregistrations [@peikert2021reproducible] from the same Markdown language.

@@

<!-- - The results of hash functions are generally not guaranteed to be stable over time. To trace back possible problems, -->

@@

We strongly discourage making reproducibility checks on complete raw data. 
This is mainly for two reasons.
First, there may arise unwanted data protection issues when raw data is (accidentally) stored, copied or published via the reproducibility JSON files.
Second, the JSON format is inefficient in terms of storage space required.
It is designed to be human-readable and conformable with versioning tools such as git.
It is not meant for storing large data and will blow up file size by a considerable factor (while at the same time losing numerical precision).
At the same time, ensuring that the data set identical to the one used in the original analysis was used, adding a check on the contents of a `data.frame`.

>>>>

Computational results, including those from statistical data analyses, are considered _reproducible_ if the same computation on the same data yields the same results if performed on a different computer or on the same computer later in time. Reproducibility is a prerequisite for replicable, robust and credible research in digital environments [@epskamp2019reproducibility; @hardwicke2018data].
Surprisingly often, results from published raw data cannot be reproduced [@artner2021reproducibility].
 Various approaches have been suggested to increase chances of reproducibility of statistical data analyses in the R language [@peikert2021reproducible; @renv2022; @chan2023rang; @nagraj2023pracpac].
 Many approaches rely on R Markdown [@rmarkdown2023].
R Markdown is a simple language, which allows mixing natural language, simple formatting instructions (e.g., what is a headline, what should appear in bold face, what are list elements) and computer code (R, python or others) in a single document [@xie2018r].
When ever the document is reproduced, all of its computer code chunks are executed and thus generate dynamic content in the document.
This is particularly interesting for quantitative research reports, as  statistical results and contents of tables and figures can be dynamically generated. 
Packages like `papaja` [@R-papaja] or `stargazer` [@R-stargazer] further extend R Markdown's capabilities to format documents (including tables and figures) in a specific journal style, such as APA style.
Also, (R) Markdown forms the basis of _executable research articles_ [@tsang2020welcome], a browser-based form of research articles that allows authors to enrich their publications with interactive elements, such as figures or results that dynamically change based on readers' input.
A particular advantage of using R Markdown for creating research reports is that it helps avoiding common threats to reproducibility of statistical results, first and foremost, copy&paste errors between results of a regular R script and a scientific report (e.g., a reported statistic or table in a Word document) [@peikert2021reproducible];
further, it is suitable to generate a variety of scientific assets other than manuscripts such as posters [@posterdown2019], presentations [@xaringan2022], resumés [@vitae2023] or preregistrations [@peikert2021reproducible] from the same Markdown language.

@@

@@

We strongly discourage making reproducibility checks on complete raw data. 
This is mainly for two reasons.
First, there may arise unwanted data protection issues when raw data is (accidentally) stored, copied or published via the reproducibility JSON files.
Second, the JSON format is inefficient in terms of storage space required.
It is designed to be human-readable and conformable with versioning tools such as git.
It is not meant for storing large data and will blow up file size by a considerable factor (while at the same time losing numerical precision).
At the same time, ensuring that the data set is identical to the one used in the original analysis was used is essential (see our previous suggestion for checkpoints in a data analysis); that is, raw data in a `data.frame` or similar R structure should be tested for reproducibility but only indirectly using fingerprints.
Note that many fitted statistical models in R also contain raw data, such as (general) linear model fits from the `stats` or `lme4` package or structural equation model fits from the `lavaan` or `OpenMx` packages.
Repeating our previous suggestion, we recommend to only subject parameter estimates and fit indices to the reproducibility checks but not variables containing fitted statistical models.
